### 2019-04-26 Results.Rmd
Add files via upload

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Loading enviroment
## Will change to a enviroment specifically containing only results.
load("C:/Users/Martin/transfer-effect-mistriage/code/globalenv.RData")
```

# Results

We analyseed data from `r sum(data.sets$multi.centre.vs.single.centre$multi.centre$.imp == 0) ` trauma patients. The high and low centre samples contains `r sum(data.sets$high.volume.vs.low.volume$high.volume$.imp==0) ` and `r sum(data.sets$high.volume.vs.low.volume$low.volume$.imp==0)` trauma patients respectively (Table 1). The metropolitan sample and the non-metropolitan sample contains `r sum(data.sets$metropolitan.vs.non.metropolitan$metropolitan$.imp==0) ` and `r sum(data.sets$metropolitan.vs.non.metropolitan$non.metropolitan$.imp==0) ` respectively (Table 2). The multi centre sample constitutes the total number of trauma patients. We identified only one valid single centre. This single centre was identified as Karolinska Sjukhuset in Stockholm and contains `r  sum(data.sets$multi.centre.vs.single.centre$single.centre.11001$.imp==0) ` trauma patients (Table 3). The data presented in each table is multiple imputed. The number of imputations used is `r number.of.imputations  `, which is equal to the maximum percentage of missing data found across the data sets.

All samples were similar regarding age, GCS, SBP and RR. The percentage of missing data in the high and low volume sampes were `r NA.info.sample$high.volume.vs.low.volume$high.volume$percent.NA`% and `r NA.info.sample$high.volume.vs.low.volume$low.volume$percent.NA`%. ...

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## LOADING ENVIROMENT
results <- readRDS("C:/Users/Martin/transfer-effect-mistriage/code/output/original.results.Rds")
## PREPARED CODE SNIPPETS
## Total patients and NA
total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
## Sample NA
na.vector <- unlist(results$NA.info.sample)
highest.percent.missing.number <- max(na.vector[na.vector<100])
highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
## Variable NA
number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
name.variable.na <- row.names( results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,] )
## Development and validation
max.imp <- max(results$original.stats$Total.imputations)
best.validation <- results$original.stats[results$original.stats$Validation.mistriage.median == min(results$original.stats$Validation.mistriage.median),]
## Comparison
best.transfer <- results$original.stats[results$original.stats$Transfer.mistriage.median == min(results$original.stats$Transfer.mistriage.median),]
worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == min(min(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median)),]

```

# Results
We analysed data from `r total.number.of.patients ` trauma patients to investigate the effects of transfer on clinical prediction models (Table 1). The total number of missing observations was `r total.number.of.na ` in the entire study cohort. The sample with the highest percentage of missing observations was the `r highest.percent.missing.name ` sample with `r highest.percent.missing.number `%. The variable with the highest number of missing observations was `r name.variable.na `, with `r number.variable.na ` missing observations, which constituted `r percent.variable.na ` % of the total observations for this variable.

Variable outliers?  
Divergent samples or variables.  
NA for predictors and outcome??  
Table 1 = Sample Characteristics table

## Development and validation
During model development, the maximum amount of imputations used was `r max.imp`, which is equal to the highest percentage of missing observations. Restricted dubic splines were implemented when modelling sysytolic blood pressure and respiratory rate, in both cases 4 knots were used. Model validation performance was obtained for each model (Table 2).
The sample with the best validation model performance was the `r best.validation$Sample.name` sample with a median mistriage rate of `r best.validation$Validation.mistriage.median` (IQR `r best.validation$Validation.mistriage.lb` - `r best.validation$Validation.mistriage.ub`). Model validation performance in general was good/poor with a median mistriage rate range of `r min(results$original.stats$Validation.mistriage.median)` - `r max(results$original.stats$Validation.mistriage.median)`.

Imputations  
Shrinkage factor?  
Optimal cut-off?  
RCS for different variables  
Bootstraps?  
Local mistriage values.  
Table 2 = Medians and IQR for validation

## Comparison
Model performance after transfer was determined in each data set (Table 3). When transferred, the model with the best performance was `r best.transfer$Sample.name` with a median mistriage of `r best.transfer$Transfer.mistriage.median` (IQR `r best.transfer$Transfer.mistriage.lb` - `r best.transfer$Transfer.mistriage.ub`). When transferred model performance was compared to the validation performance in the same sample, the transferred models generally performed worse/better/same than their corresponding local models (Table 4). The highest decline in performance was found in the `r worst.transfer$Sample.name` sample, with a median mistriage difference of `r worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median` (IQR `r worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.lb` - `r worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.ub`), meaning that this model was the most negativly affected by being transferred. In clinical terms, this model transfer means that among 100 trauma patients, `r abs(worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median) * 100` would be wrongly classified as major or minor trauma.

Comparison model performances.  
Most? Less?   
Significance! P-values.  
Table 3 = Medians and IQR for transfer.  
Table 4 = Medians and IQR for the difference in performance
